Individual Stellar Halos of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-10-17 draft/response_paper_I.md

We also add a new bullet point to summarize our results on using the aperture masses to trace the in-situ and ex-situ components.

-----

## Figures:

> Fig.1: delate the last sentence, this is not a description of the figure.```

It has been removed based on the referee's suggestion.

> Remove Fig.3 and left panel of Fig 5:See the above comments on avoiding discussion on the cModel.

As we have been explained multiple times above, in our opinion, the comparisons with CModel are not only a crucial technical point, but also the key result of this paper.  We propose to keep these two figures and most of the relevant text.

> Left panel of Fig.8 is a COPY of Fig.6, please, merge them

As we explained above, the right panel of Figure 8 serves a different purpose in the discussion section compared to Figure 6.  Also, merging these two figures will make it very busy and hard to see the comparisons in the inner region.  Therefore, we think it should be Ok to keep the right panel of Figure 8 as is.
